\begin{flushleft}
	\begin{itemize}

		\begin{enumerate}
			\item (Re)boot the system.
			\item Interrupt the boot loader menu countdown by pressing any key.
			\item Move the cursor to the entry to be started.
			\item \textbf{Press e} to edit the current entry.
			\item Move the cursor to the line that starts with linux16. This is the kernel command line.
			\item Append \textbf{rd.break} (this will break just before control is handed from the initramfs to the actual system).
			\item Press \textbf{Ctrl+x} to boot with these changes.
		\end{enumerate}
		At this point, a root shell will be presented, with the root file system for the actual system 	mounted read-only on /sysroot.
		\newline
		\newline
		To recover the root password from this point, use the following procedure:
		
		\begin{enumerate}
			\item Remount /sysroot as read-write.
			\begin{tcolorbox}[breakable,notitle,boxrule=-0pt,colback=black,colframe=black]
				\color{green}
				\fontdimen2\font=1em
				switch\_root:/\# \textbf{mount -o remount,rw /sysroot}
				\fontdimen2\font=4pt
			\end{tcolorbox}
			\item Switch into a chroot jail, where /sysroot is treated as the root of the file system tree.
			\begin{tcolorbox}[breakable,notitle,boxrule=-0pt,colback=black,colframe=black]
				\color{green}
				\fontdimen2\font=1em
				switch\_root:/\# \textbf{chroot /sysroot}
				\fontdimen2\font=4pt
			\end{tcolorbox}
			\item Set a new root password:
			\begin{tcolorbox}[breakable,notitle,boxrule=-0pt,colback=black,colframe=black]
				\color{green}
				\fontdimen2\font=1em
				sh-4.2\# \textbf{passwd root}
				\fontdimen2\font=4pt
			\end{tcolorbox}
			\item Make sure that all unlabeled files (including /etc/shadow at this point) get relabeled during boot.
			\begin{tcolorbox}[breakable,notitle,boxrule=-0pt,colback=black,colframe=black]
				\color{green}
				\fontdimen2\font=1em
				sh-4.2\# \textbf{touch /.autorelabel}
				\fontdimen2\font=4pt
			\end{tcolorbox}
		
			\item Type \textbf{exit} twice. The first will exit the \textbf{chroot} jail, and the second will exit the initramfs debug shell.
		\end{enumerate}
	
		At this point, the system will continue booting, perform a full SELinux relabel, then reboot again.
	\end{itemize}
\end{flushleft}

\newpage